\Large \bf \projtitle

### 2015-05-08 doc/paper/paper.tex
Update

The \zbf client-side code runs purely in the browser, and is completely transparent
to the user. The user does not have to install any application on their
computer to obtain desired resources peer-to-peer. As a result, the \zbf client
code only runs when a user is currently visiting the website, therefore adding
no burden to the user from constant background processes.

In designing \zbf, we took into consideration the unique problems presented
by browser-to-browser content streaming. Website visitor churn is often very
high with any type of website; our system had to be robust under these common
conditions. \zbf forms peer-to-peer connections quickly and immediately streams
requested resources through these data channel connections. \zbf also recovers
quickly from data request failures; the \zbf data chunking component minimizes
latency from these failures and quickly retries resource requests with other
peers.

@@

\zbf divides assets into chunks; chunks are individually requested and
sent between peers. We use a standard chunk size of 10240 bytes in our
implementation; preliminary tests showed this chunk size to be reasonable.
When a client asks for a resource, the download manager for that client
determines the number of chunks for that resource from the resource's total size.
The download manager then evenly distributes requests for these chunks
among the peers with the resource.

>>>>

The \zbf client-side code runs purely in the browser and is completely
transparent to the user. The user does not have to install any application on
their computer to obtain desired resources peer-to-peer. As a result, the \zbf
client code only runs when a user is currently visiting the website, adding no
burden to the user from constant background processes.

In designing \zbf, we took into consideration the unique problems presented
by browser-to-browser content sharing. Website visitor churn is often very
high with any type of website; our system had to be robust under these common
conditions. \zbf forms peer-to-peer connections quickly and immediately streams
requested resources through these data channel connections. \zbf also recovers
quickly from data request failures; the \zbf data chunking component minimizes
latency from these failures and quickly retries resource requests with other
peers.

@@

\zbf divides assets into chunks; chunks are individually requested and
sent between peers. We use a standard chunk size of 25 KB in our
implementation; preliminary tests showed this chunk size to be reasonable.
When a client asks for a resource, the download manager for that client
determines the number of chunks for that resource from the resource's total size.
The download manager then evenly distributes requests for these chunks
among the peers with the resource.
